### 2015-02-05 fundamentals/examples.tex
more details about example simulation.

Results of some simple recycle scenarios run in \Cyclus follow. Beginning with a single
reactor simulation, open (no recycle), modified open, and closed (infinite-pass recycle) 
fuel cycles are compared to illustrate the resolution possible with \Cyclus.  The simulation
is then expanded to include multiple reactors in the same set of fuel cycles to demonstrate
the system-scale convergence to continuous material flow models.

Because material is tracked as discrete objects, single-pass recycle using \gls{MOX} 
fuel is easy to implement in \Cyclus.  The \gls{MOX} simulation includes one provider of fresh
\gls{UOX} fuel, one recycled fuel fabrication facility, one reactor, one separations
facility, and one repository. The simulation has a duration of 1100 months and a \TODO{??-month stepsize}.

The \Class{BatchReactor} archetype from \Cycamore has the ability to accept
fuel materials from an arbitrary number of different sources, delineated by
commodity. Custom, non-uniform preferences can be set for each different fuel
commodity.  The \gls{DRE} enables a reactor to
preferentially accept recycled \gls{MOX} fuel over fresh \gls{UOX} fuel.  In this
simulation, the
\Class{BatchReactor} was configured to run with a 3 batch core on 18 month cycles and
a 2-month refueling period.  Adjusting and setting parameters such as these is
as simple as editing numbers in an input file such as:

\begin{lstlisting}[language=xml]
  ...
  <BatchReactor>
      ...
      <processtime>18</processtime>
      <nbatches>3</nbatches>
      <batchsize>20000</batchsize>
      <refueltime>2</refueltime>
      ...
  </BatchReactor>
  ...
\end{lstlisting}

The \Class{Source} and \Class{Sink} archetypes from \Cycamore have been used as a
source of fresh, enriched uranium and a repository, respectively. A simple
custom recycled fuel fabrication facility was also used, which mixes fissile 
and fertile streams to match target fuel compositions as closely
as possible.  The method used for this matching is approximately the same as
that used by the \gls{COSI} fuel cycle simulator \TODO{cite COSI equivalence
method}. The material flows for this simulation are shown below in Figure
\ref{fig:flowmodopen}.

\begin{figure}[H]
\begin{center}
\includegraphics{./images/flow-mod-open-1.eps}
\end{center}
\caption{Modified open 1-pass \gls{MOX} recycle fuel cycle material flows.}
\label{fig:flowmodopen}
\end{figure}

Changing this to a fully closed fuel cycle entails only a one-word change in the input file
regarding the output commodity for the spent \gls{MOX} fuel of the
\Class{BatchReactor}:

\begin{lstlisting}[language=diff]
  --- mod-open-1.xml	2014-10-08 08:31:33.892523173 -0500
  +++ closed-1.xml	2014-10-08 08:31:33.892523173 -0500
  @@ -108,7 +108,7 @@
           <fuel>         
             <incommodity>mox_fuel</incommodity>
             <inrecipe>lwr_mox_fuel</inrecipe>
  -          <outcommodity>spent_mox</outcommodity>
  +          <outcommodity>spent_fuel</outcommodity>
             <outrecipe>mox_spent_fuel</outrecipe>
           </fuel>
\end{lstlisting}

This results in the material flows in Figure \ref{fig:flowclosed}. Note
that the \Class{BatchReactor} always transmutes fuel into the same
composition, so the nuclide level flows are unrealistic for the full, 
multi-pass
recycle case.

@@

Because facilities are represented individually and
transact discrete materials as discrete events, realistic non-uniform patterns in facility behavior
that affect total system behavior are observed using \Cyclus, which is uncommon 
for fleet-based, continuous material flow models.

@@

The open, modified open, and closed scenarios can easily be modified to have
several reactors with staggered refueling times. The plutonium buildup
for these three multi-reactor variations is shown in Figure
\ref{fig:puseriesn}. As the number of
reactors increases, the behavior of the system approaches a more steady
average reminiscent of continuous material flow models.

>>>>

This section will discuss the creation and results of a few simple fuel cycle
simulations to help illustrate the flexibility of \Cyclus. These simulations
are designed to illustrate Cyclus' capability.  Many simplifying assumptions
have been made with respect to material compositions, fuel transmutation, and
others. The three fuel cycles examined are:

\begin{enumerate}
    \item Once through (no recycle) 
    \item Modified open (1-pass recycle)
    \item closed (infinite-pass recycle)
\end{enumerate}

For each of these fuel cycles, a 1,100 month \Cyclus simulation with only a
single reactor is run in addition to a simulation with 10 reactors with
staggered refueling times.  As the number of staggered-cycle reactors
increases the system converges toward continuous material flow results.
\Cyclus flexibility allows this transition to be examined.  The facilities
used in these simulations are:

\begin{itemize}

    \item \textbf{Reactor} (\Class{cycamore::Reactor}): This is a reactor
        model that requests any number of input fuel types and uses static
        compositions to transmute them to after they are burnt and discharged
        from the core.  Due to the static spent fuel compositions spent fuel
        compositions become "incorrect" as the input fuel diverges from the
        fixed, expected input composition. The reactor was configured to model
        a light water reactor with a 3 batch core (20,000 kg HM per batch)
        operating on an 18 month cycle with a 2 month refuel time.  The
        reactor was also configured to take in either enriched UOX fuel or
        recycled MOX fuel - preferring the latter if available.

    \item \textbf{Recycled Fuel Fabrication} (\Class{cycamore::Fab}): This
        facility requests depleted uranium and separated fissile material and
        mixes them together into recycled MOX fuel that it offers to
        requesters.  The streams are mixed using a D-factors approach
        \TODO{add D-factors citation} in an attempt to match simple neutronics
        properties of an ideal target fuel composition.

    \item \textbf{Separations} (\Class{cycamore::Separations}): This facility
        takes in all kinds of spent fuel and separates it into plutonium and
        waste streams with some efficiency (0.99 was used for these
        simulations).  Up to 60,000 kg of Pu can be separated per month.

    \item \textbf{Repository} (\Class{cycamore::Sink}): This is an
        infinite-capacity facility that can take in all types of material
        including separations waste streams and spent reactor fuel.

    \item \textbf{UOX Fabrication} (\Class{cycamore::Source}): This facility
        provides enriched UOX fuel as requested with infinite capacity.

    \item \textbf{DU Source} (\Class{cycamore::Source}): This facility provides
        depleted uranium as requested with infinite capacity.

\end{itemize}

For the once through case, the \Class{Reactor} was set to offer all spent fuel
as waste.  For the modified open case, the \Class{Reactor} offerred spent UOX
into a spent fuel market where it is preferrentially sent to separations, but
spent MOX is still offerred as waste.  In the closed case, the \Class{Reactor}
offers all spent fuel into a spent fuel market. Because the separations
facility requests spent fuel with a higher preference than the repository, it
is sent there if possible.  All these preferences are easy to adjust and
\Cyclus will dynamically handle supply constraints and non-uniform preference
resolution.  It is notable that separations and recycle fuel fabrication
capacity is deployed identically in all simulations.  In the once-through
case, the recycling loop never acquires material, and so reactors always
receive fresh UOX fuel.  In the modified open case, the recycle loop only
acquires spent UOX.  The \gls{DRE} ensures everything operates smoothly in all
cases.

Cyclus' discrete materials make single-pass recycle easy to implement.  The
reactors keep track of fuel as discrete batches. A reactor remembers where it
received each batch from.  If a batch was received from the recycled fuel
fabrication facility, it does not offer it to separations and instead sends it
to the repository directly.  The material flows for the modified open case are
shown in Figure \ref{fig:flowmodopen}.

\begin{figure}[H]
\begin{center}
\includegraphics{./images/flow-mod-open-1.eps}
\end{center}
\caption{Modified open 1-pass \gls{MOX} recycle scenario material flows.}
\label{fig:flowmodopen}
\end{figure}

Changing the scenario from a modified open fuel cycle to a closed fuel cycle
requires only a one-word change in the input file regarding the output
commodity for the spent \gls{MOX} fuel of the \Class{Reactor}:

\begin{lstlisting}[language=diff]
     <fuel>         
       <incommodity>mox</incommodity>
  -    <outcommodity>waste</outcommodity>
  +    <outcommodity>spent_fuel</outcommodity>
       <inrecipe>mox_resh_fuel</inrecipe>
       <outrecipe>mox_spent_fuel</outrecipe>
     </fuel>
\end{lstlisting}

This results in the material flows in Figure \ref{fig:flowclosed}.  A
similarly trivial change was used to switch from the once through to a
modified open fuel cycle.  Note that the \Class{Reactor} always transmutes
fuel into fixed compositions, so nuclide-specific flows become
somewhat unrealistic in the fully closed cycle case.

@@

Because facilities are represented individually and transact discrete
materials as discrete events, realistic non-uniform patterns in facility
behavior that affect total system behavior are observed using \Cyclus.

@@

Figure \ref{fig:puseriesn} shows plutonium buildup for the 10-reactor
simulations of the open, modified open, and closed scenarios.  As the number
of reactors (with staggered refueling) increases, the behavior of the system
approaches a more steady average reminiscent of continuous material flow
models.
